Enhancing Adversarial Robustness for Deep Metric Learning

### 2021-11-09 robdml.tex
tex

Additionally, it is noted that a sample triplet will be augmented into a
sextuplet (both benign and adversarial examples) during adversarial training.
%
In this case, the \emph{intra-class} structure can be enforced, has been
neglected by existing methods.
%
Since some existing attacks aim to change the sample rankings in the same
class~\cite{advrank},
%
we propose a simple \emph{intra-class} structure loss term for adversarial
training, which is expected to further improve robustness.

@@

% contributions
In brief, our contributions include:
%
\begin{enumerate}[nosep, noitemsep, leftmargin=*]
	%
	\item {\textit{Hardness Manipulation}} (HM) is proposed as a flexible and
		efficient tool to create adversarial example triplets for subsequent
		adversarial training of DML model.
		%
	\item \textit{Linear Gradual Adversary} (LGA) is proposed as a
		pseudo-hardness function for HM, which incorporates our empirical
		observations and can balance the training objectives during the
		training process.
		%
	\item \textit{Intra-Class Structure} (ICS) loss term is proposed to further
		improve the DML model robustness, while such possibility is neglected
		by existing methods. 
		%
\end{enumerate}

@@

\noindent\textbf{III. Intra-Class Structure.}
%
Although independent to HM, ACT is incompatible with $L_\text{ICS}$ as it does
not create an adversarial anchor.
%
Thus, we validate this loss term with HM.
%
As shown in \cref{tab:ics} and \cref{fig:ics}, $L_\text{ICS}$ consistently
leads to a higher efficiency in gaining robustness, while retaining a
good trade-off between ERS and R@1.

>>>>

Additionally, it is noted that a sample triplet will be augmented into a
sextuplet (both benign and adversarial examples) during adversarial training.
%
In this case, the \emph{intra-class} structure can be enforced, which has been
neglected by existing methods.
%
Since some existing attacks aim to change the sample rankings in the same
class~\cite{advrank},
%
we propose a simple \emph{intra-class} structure loss term for adversarial
training, which is expected to further improve robustness.

@@

% contributions
In brief, our contributions include proposing:
%
\begin{enumerate}[nosep, noitemsep, leftmargin=*]
	%
	\item {\textit{Hardness Manipulation}} (HM) as a flexible and efficient
		tool to create adversarial example triplets for subsequent adversarial
		training of DML model.
		%
	\item \textit{Linear Gradual Adversary} (LGA) as a Graduate Adversary, \ie,
		a pseudo-hardness function for HM, which incorporates our empirical
		observations and can balance the training objectives during the
		training process.
		%
	\item \textit{Intra-Class Structure} (ICS) loss term to further improve
		model robustness (especially intra-class-wise), while such structure is
		neglected by existing methods. 
		%
\end{enumerate}

@@

\noindent\textbf{III. Intra-Class Structure.}
%
$L_\text{ICS}$ is independent to HM, but is not incompatible with ACT as it
does not create adversarial anchor.
%
Thus, we validate this loss term with HM.
%
As shown in \cref{tab:ics} and \cref{fig:ics}, $L_\text{ICS}$ consistently
leads to a higher efficiency in gaining robustness (especially
intra-class-wise), while retaining an acceptable trade-off in R@1.
